% !TeX root = ../../main.tex

%% Thanks Professor Lau and Professor Rui Wang
\revise{
    As a student of the Joint Education Programme for PhD offered by The University of Hong Kong (HKU) and Southern University of Science and Technology (SUSTech), I would like to express my heartfelt gratitude to my supervisors, Prof. Francis. C. M. Lau in HKU and Prof. Rui Wang in SUSTech, for their supervision as well as to HKU and SUSTech for their support for my research studies in HKU and SUSTech.
}%
% First and foremost, I would like to express my sincere gratitude to my supervisor, Prof. Francis C.M. Lau, and my co-supervisor, Prof. Rui Wang.
Their insightful expertise, unreserved guidance and persistent commitments always accompanies me throughout the long run of pursuing the Ph.D. degree.
Thanks for all your stringent requirements and meaningful commentaries, which shapes my research sense and attitude.
It is my great honor to be their student.
%% Thanks Professor Haisheng Tan
I would also like to express my thankfulness to Prof. Haisheng Tan for his invaluable instruction and suggestions throughout my research.
It would be impossible for me to get up to the research more quickly without his proper and effective feedbacks on paper writing.

%% Thanks support from collaborators and advisors
Additionally, I would like to extend my sincere appreciation and gratitude to my excellent collaborators, Dr. Zhenhua Han, Prof. Shuai Wang, Mr. Liangkai Zhou and Mr. Zijian Zhang, for their valuable feedback and insights.
I would also like to pay tribute to all my friends who support me so far.
Their kindness, exceptional guidance and constant encouragement have made this journey more enjoyable.
I consider myself fortunate to have received support from such distinguished individuals.
%% Thanks Professor Choli Wang and the students
I would like to express my gratitude to Professor Choli Wang for the opportunity to serve as a teacher assistant.
I have learned a lot from the teaching experience, and I am grateful for the opportunity to have my eyes opened to new ideas and perspectives.

%% Thanks for the joint program between HKU and SUSTech
I express my sincere gratitude to have the chance to join the joint program between HKU and SUSTech.
The ongoing supports and feedbacks from the Department of Computer Science at HKU and the Department of Electronic and Electrical Engineering from SUSTech have been invaluable to my research. I am thankful for the opportunity to work alongside such talented individuals.
Furthermore, I acknowledge the financial support I received which enabled me to pursue my research in a full-time capacity.

%% Thanks to my parents
Last but not least, I would like to express my sincere gratitude to my parents for their unconditional love and support throughout my academic journey.
They have been my constant source of love, support, and inspiration throughout my life, and I am forever grateful for their unwavering encouragement.
Their love, support, and understanding has been a constant source of strength throughout the long and sometimes challenging process of obtaining a degree.
