% !TeX root = ../../main.tex

The full publication list during my Ph.D. study is listed as follows.
There are four publications (1,2,3,7) presented in thesis.

% [1]
\cite{msn2020-hong} \textbf{Yuncong Hong}, Bojie Lv, Rui Wang, Haisheng Tan, Zhenhua Han, Hao Zhou, Francis C. M. Lau, ``Online Distributed Job Dispatching with Outdated and Partially-Observable Information,'' 2020 16th International Conference on Mobility, Sensing and Networking (MSN), Tokyo, Japan, 2020.

% [2]
\cite{jiot2021-hong} \textbf{Yuncong Hong}, Bojie Lv, Rui Wang, Haisheng Tan, Zhenhua Han, Francis C. M. Lau, ``Distributed Job Dispatching in Edge Computing Networks With Random Transmission Latency: A Low-Complexity POMDP Approach,'' in IEEE Internet of Things Journal, vol. 9, no. 6, pp. 4152-4167, 15 March, 2022.

% [3]
\cite{tcom2023-hong} \textbf{Yuncong Hong}, Bojie Lv, Shuai Wang, Haisheng Tan, Francis C. M. Lau, ``FedCars: A Data-Driven Uplink Scheduling Framework for Efficient In-Vehicle Federated Edge Learning,'' Submitted to IEEE Transactions on Communications, 2023.

% [4]
\cite{icra2021-hong} Zijian Zhang, Shuai Wang, \textbf{Yuncong Hong}, Liangkai Zhou and Qi Hao, ``Distributed Dynamic Map Fusion via Federated Learning for Intelligent Networked Vehicles,'' 2021 IEEE International Conference on Robotics and Automation (ICRA), Xi'an, China, 2021.

% [5]
\cite{tcom2022-hong} Shuai Wang, \textbf{Yuncong Hong}, Rui Wang, Qi Hao, Yik-Chung Wu and Derrick Wing Kwan Ng, ``Edge Federated Learning via Unit-Modulus Over-The-Air Computation,'' in IEEE Transactions on Communications, vol. 70, no. 5, pp. 3141-3156, May 2022.

% [6]
\cite{tvt2020-hong} Liangkai Zhou, \textbf{Yuncong Hong}, Shuai Wang, Ruihua Han, Dachuan Li, Rui Wang, Qi Hao, ``Learning Centric Wireless Resource Allocation for Edge Computing: Algorithm and Experiment,'' in IEEE Transactions on Vehicular Technology, vol. 70, no. 1, pp. 1035-1040, Jan. 2021.

% [7]
\cite{jcin2020-hong} Bojie Lyu, \textbf{Yuncong Hong}, Haisheng Tan, Zhenhua Han, Rui Wang, ``Cooperative Jobs Dispatching in Edge Computing Network with Unpredictable Uploading Delay,'' in Journal of Communications and Information Networks, vol. 5, no. 1, pp. 75-85, March 2020.

% [8]
\cite{commag2022-hong} Shuai Wang, Ruihua Han, \textbf{Yuncong Hong}, Qi Hao, Miaowen Wen, Leila Musavian, Shahid Mumtaz, Derrick Wing Kwan Ng, ``Robotic Wireless Energy Transfer in Dynamic Environments: System Design and Experimental Validation,'' in IEEE Communications Magazine, vol. 60, no. 3, pp. 40-46, March 2022.

% [9]
\cite{tnet2022-hong} Zhenhua Han, Haisheng Tan, Rui Wang, \textbf{Yuncong Hong}, Francis C. M. lau, ``Efficient Online Learning Based Cross-Tier Uplink Scheduling in HetNets,'' in IEEE/ACM Transactions on Networking, vol. 30, no. 6, pp. 2389-2402, Dec. 2022.
